%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass[twocolumn,11pt]{report}
\usepackage[a4paper,margin=1in,landscape]{geometry}
\usepackage{xcolor, soul}
\usepackage{hyperref}
\hypersetup{
     colorlinks = true,
     urlcolor = blue,
     urlbordercolor=blue,% hyperlink borders will be red
}

\makeatletter
\Hy@AtBeginDocument{%
  \def\@pdfborder{0 0 1}% Overrides border definition set with colorlinks=true
  \def\@pdfborderstyle{/S/U/W 1}% Overrides border style set with colorlinks=true
                                % Hyperlink border style will be underline of width 1pt
}
\makeatother

\begin{document}

\section*{\huge Danila Danko}

Software developer

\section*{Contacts}
\begin{itemize}
     \item GitHub: \href{https://github.com/deemp}{deemp}
     \item Telegram: \href{https://t.me/daniladanko}{@daniladanko}
     \item Email: br4ch1st0chr0n3@gmail.com
\end{itemize}

\section*{Summary}
Functional programmer.
Implemented back ends in Haskell and Python, front ends in PureScript and TypeScript.
Used Nix and Bash extensively for setting up projects infrastructure.
Have experience with Docker, Kubernetes, Pulumi, Helm.
Worked with PostgreSQL, SQLite, and studied SQL.
Managed the development of an open-source project.
Willing to work on interesting products in a team of professional developers.

% TODO value for company

\section*{Education}
\begin{itemize}
     \item \textbf{Innopolis University} (2019-2023) \newline Computer Science

     \item \textbf{Innopolis University} (2023-2025) \newline MS in Software Enginering

\end{itemize}

\section*{Work experience}

\begin{itemize}
     \item \textbf{Innopolis University} (2021-2022) \newline developer in the Polystat project

\end{itemize}
\newpage

\section*{Interests}
\begin{itemize}
     \item Back-end development
     \item DevOps
     \item Contributing to open-source
     \item Functional programming
\end{itemize}

\section*{Projects}

\begin{itemize}
     \item \href{https://github.com/deemp/elibrary#readme}{elibrary} - electronic library of the Innopolis University (Python, TypeScript, Nix, Docker)
     \item \href{https://github.com/nix-community/nix-vscode-extensions#readme}{nix-vscode-extensions} - Nix expressions for almost all VSCode extensions (Haskell, Nix)
     \item \href{https://github.com/deemp/flakes#readme}{flakes} - Nix flakes for my projects
     \item \href{https://github.com/deemp/projects#readme}{projects} - monorepo with my projects in Haskell and other languages.
     \item \href{https://github.com/breaking-news-org/back-end#readme}{breaking-news-org/back-end} - news site back-end (Haskell, Pulumi, Kubernetes, Nix, PostgreSQL)
     \item \href{https://github.com/objectionary/try-phi#readme}{try-phi} - online interactive interpreter of EO and $\varphi$-calculus (Haskell, TypeScript, PureScript)
     \item \href{https://github.com/deemp/servant-queryparam#readme}{servant-queryparam} - plugins for servant (a Haskell webservices API library)
     \item \href{https://github.com/deemp/clerk#readme}{clerk} - declaratively generate spreadsheets (Haskell)
     \item \href{https://github.com/deemp/arigame#readme}{arigame} - an arithmetics game (PureScript)
     \item \href{https://github.com/deemp/projects/tree/main/haskell/ts-serializable-test#readme}{ts-serializable-test} - code generator for testing ts-serializable (Haskell, TypeScript)
\end{itemize}

\end{document}
